Formalizing Stack Safety as a Security Property

### 2021-09-29 submission4/main.tex

\caption{A confidentiality violation\ifspace\apt{Could save space by not
    repeating C or assemly code for {\tt main}.}\fi}
\label{fig:conf1}
\end{figure}

@@

In Figure~\ref{fig:conf1} we see how noninterference applies to this scenario.
At instruction 10, we
create an imaginary {\em variant}
state with arbitrary values\ifaftersubmission\bcp{IMO, it would be easier to
  understand if we chose concrete values for the examples}\sna{FWIW I agree in
  theory, but it looks bad every time I try it.}\fi~(\(v_0\), etc.),
in place of the actual values ($42$, ...) that should
be hidden from {\tt f}; we show the evolving stack memory of the variant in the second column.
At instruction 11, the callee's variable, {\tt z},
changes to 42 in the primary trace, but
in the variant trace it instead might have any value \(v_0\). If \(v_0 \neq 42\), then the variant
has behaved differently than the primary, violating confidentiality.

>>>>

\caption{A confidentiality violation\bcp{tighten so it doesn't spill into margins}\ifspace\apt{Could save space by not
    repeating C or assemly code for {\tt main}.}\fi}
\label{fig:conf1}
\end{figure}

@@

In Figure~\ref{fig:conf1} we see how noninterference applies to this scenario.
At instruction 10, we
create an imaginary {\em variant}
state with arbitrary values~%
%\ifaftersubmission\bcp{IMO, it would be easier to
%  understand if we chose concrete values for the examples}\sna{FWIW I agree in
%  theory, but it looks bad every time I try it.}\fi
(\(v_0\), etc.),
in place of the actual values ($42$, ...) that should
be hidden from {\tt f}; we show the evolving stack memory of the variant in the second column.
At instruction 11, the callee's variable, {\tt z},
changes to 42 in the primary trace, but
in the variant trace it instead might have any value \(v_0\). If \(v_0 \neq 42\), then the variant
has behaved differently than the primary, violating confidentiality.
